### 2012-01-16 paper.tex
Figures are now MUCH closer to be of publishable quality

The period of the oscillations ranges from a few seconds (the time-constant of the reactor) up to more than an hour. A typical slow is oscillation is seen in figure~\ref{fgr:full_oscillation} where we see the typical pattern going from almost no activity slowly up towards $\sim$50\% conversion at which point the sample light off to full conversion almost instantiously where after a short peiod of time the sample again de-activates.
% an example of a two-column figure, remember that the graphics should be included where it is first referenced
\begin{figure*}
  \centering
  \includegraphics[height=7cm]{single_full_oscillation.png}
  \caption{A full oscillation first showing a steep ignition of the sample followed by an almost imidiately de-activation of the sample. For the next 65\,minutes the sample slowly recovers activity until it again lights off completely.}
  \label{fgr:full_oscillation}
\end{figure*}

If a sample is leaved for long periods of time, it keep performing sustained oscillations, but with longer and longer periods. In the beginning the period is very stable and sligtly increasing but after a few days, the periods becomes more and more noisy although still maintaining the trend of longer and longer periods. Figure~\ref{fgr:full_oscillation} shows a summary of the periods of a sample oscillating for 4 days. 
% an example of a single-column figure, remember that the graphics should be included where it is first referenced
\begin{figure}[h]
\centering
  \includegraphics[height=7cm]{summary_of_long_measurement.png}
  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample a total for 439 oscillations in 4 days.}
  \label{fgr:long_measurement}
\end{figure}

Extracts of the mass-spectrometry from the very beginning, the middle and towards the end of the experiments is shown in figure~\ref{fgr:extracts}, it is evident that the oscillations are getting more and more irregular as times goes on, towards the end, it is also clearly visible how the smaller oscillations are taking place at a much higher frequency than the full on-off cycles, which is most likely the explanation for the increasing scatter in the period summary.
% an example of a two-column figure, remember that the graphics should be included where it is first referenced
\begin{figure*}
  \centering
  \includegraphics[height=7cm]{extracts_from_very_long_oscillation.png}
  \caption{Extracts from the 4 day long experiment.}
  \label{fgr:extracts}
\end{figure*}

>>>>

The period of the oscillations ranges from a few seconds (the time-constant of the reactor) up to more than an hour. A typical slow is oscillation is seen in figure~\ref{fgr:full_oscillation} where we see the typical pattern going from almost no activity slowly up towards $\sim$50\% conversion at which point the sample light off to full conversion almost instantiously where after a short peiod of time the sample again de-activates.
% an example of a two-column figure, remember that the graphics should be included where it is first referenced
\begin{figure*}
  \centering
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation first showing a steep ignition of the sample followed by an almost imidiately de-activation of the sample. For the next 65 minutes the sample slowly recovers activity until it again lights off completely.}
  \label{fgr:full_oscillation}
\end{figure*}

If a sample is leaved for long periods of time, it keeps performing sustained oscillations, but with longer and longer periods. In the beginning the period is very stable and sligtly increasing but after a few days, the periods becomes more and more noisy although still maintaining the trend of longer and longer periods. Figure~\ref{fgr:full_oscillation} shows a summary of the periods of a sample oscillating for 4 days. 
% an example of a single-column figure, remember that the graphics should be included where it is first referenced
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{summary_of_long_measurement.png}
  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
  \label{fgr:long_measurement}
\end{figure}

Extracts of the mass-spectrometry from the very beginning, the middle and towards the end of the experiments is shown in figure~\ref{fgr:extracts}, it is evident that the oscillations are getting more and more irregular as times goes on, towards the end, it is also clearly visible how the smaller oscillations are taking place at a much higher frequency than the full on-off cycles, which is most likely the explanation for the increasing scatter in the period summary.
% an example of a two-column figure, remember that the graphics should be included where it is first referenced
\begin{figure}[h]
  \centering
  \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
  \caption{Extracts from the 4 day long experiment.}
  \label{fgr:extracts}
\end{figure}
